\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[font={small,it}]{caption}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{pdfpages}
\usepackage{natbib}
\usepackage{graphicx}
\usepackage{float}
\usepackage{url}
\usepackage{nameref}
\graphicspath{{../}}
\bibliographystyle{agsm}
\hyphenation{Vonnegut}

\title{\textbf{SCC.421 Dissertation Proposal: \\ Examining Changes to ``Good'' Code Style Over Time}}
\author{
Luca Davies \\ M.Sci. (Hons.) Computer Science (with Industrial Experience)}
\date{13th March 2021}

\begin{document}
\maketitle

\newpage
\section*{Declaration}
    I certify that the material contained in this dissertation is my own work and does not contain unreferenced or unacknowledged material. I also warrant that the above statement applies to the implementation of the project and all associated documentation. Regarding the electronically submitted work, I consent to this being stored electronically and copied for assessment purposes, including the School’s use of plagiarism detection systems in order to check the integrity of assessed work. \\
    I agree to my dissertation being placed in the public domain, with my name explicitly included as the author of the work. \\
    
    \noindent
    Name: Luca Davies\\
    Date: 01/06/2021
\newpage
\section*{Abstract}
    This report examines the ever-changing code styles and best practices for a number of popular programming languages over the course of the last  twenty to thirty year. This covers the time from the inception and early years of some of the world's most widely used programming languages.
    \newline
    \newline
    [Is there any working docs?]
\newpage
\tableofcontents
\newpage

% https://www.joelonsoftware.com/2005/05/11/making-wrong-code-look-wrong/

\section{Introduction}
    \subsection{Overview}
    \subsection{Aims \& Objectives}
        The aims of this report are as such:
        \begin{itemize}
            \item 1
            \item 2
            \item 3
            \item 4
            \item 5
        \end{itemize}
    \subsection{Report Structure}
        The remainder of this report will discuss ...
\newpage
\section{Background}
\label{sec:background)}
\section{Current Standards}
        []
\section{Real-world Examples}
    []
\section{Historic Changes}
    []
\section{Conclusion}
\label{sec:conclusion}
    []
    \subsection{Review of Aims}
        The following list repeats the aims presented at the start of this report, with each aim followed by an overview of relevant results obtained.
        \begin{itemize}
            \item \textcolor{gray}{\textit{[]}}
                []
            \item \textcolor{gray}{\textit{[]}}
                []
            \item \textcolor{gray}{\textit{[]}}
                []
            \item \textcolor{gray}{\textit{[]}}
                []
            \item \textcolor{gray}{\textit{}}
                []
        \end{itemize}
    \subsection{Reflections}
        []
    \subsection{Negative Impacting Circumstances}
        The on-going coronavirus pandemic is still very much a factor in the lives us all
    \subsection{Future Research}
        []
    \subsection{Closing Statement}
        []
\bibliography{ref}
\newpage
\section*{Appendix}
    \subsection*{Appendix 1: []}
        []
    \subsection*{Appendix 2: []]}
        []
\end{document}
